### 2021-08-03 yfcc100m/paper/vldb2021/acks.tex
Update tex files for camera ready

\section{Acknowledgments}

We would like to thank the many people that made this project possible and
helped us through the process, as this work is the results of many efforts.
We want to specially thank our senior technologists Nilesh Jain and 
Ravi Iyer for their full support and input during the duration of the project.
We want to specially acknowledge Philip Lantz and Vishakha Gupta for their help
with PMGD, key to loading large datasets into VDMS.
We want to thank Jim Blakley for his input during the various 
phases of our project, and for advocating and promoting VDMS.
We want to acknowledge the Intel Labs VDMS team for their efforts
open-sourcing and maintaining the system.
We want to thank Jason Gardner for his helping in setting up many of 
the servers and infrastructure needed to conduct our experiments.

>>>>

\begin{acks}
We would like to thank the many people that made this project possible and
helped us through the process, as this work is the results of many efforts.
We want to specially thank our senior technologists Nilesh Jain and
Ravi Iyer for their full support and input during the duration of the project.
We want to specially acknowledge Philip Lantz and Vishakha Gupta for their help
with PMGD, key to loading large datasets into VDMS.
We want to thank Jim Blakley for his input during the various
phases of our project, and for advocating and promoting VDMS.
We want to acknowledge the Intel Labs VDMS team for their efforts
open-sourcing and maintaining the system.
We want to thank Jason Gardner for his helping in setting up many of
the servers and infrastructure needed to conduct our experiments.
\end{acks}

### 2021-08-03 yfcc100m/paper/vldb2021/legal.tex
Update tex files for camera ready

\scriptsize
\begin{framed}
\noindent \textbf{Notices \& Disclaimers}

\copyright  Intel Corporation.  Intel, the Intel logo, and other Intel marks are 
trademarks of Intel Corporation or its subsidiaries.  
Other names and brands may be claimed as the property of others.

Performance results are based on testing as of dates shown in configurations 
and may not reflect all publicly available security updates.  
See backup for configuration details.  
No product or component can be absolutely secure.

Your costs and results may vary.

Intel technologies may require enabled hardware, software or service activation.

Software and workloads used in performance tests may have been optimized for 
performance only on Intel microprocessors.  
Performance tests, such as SYSmark and MobileMark, are measured using specific 
computer systems, components, software, operations and functions.  
Any change to any of those factors may cause the results to vary.  
You should consult other information and performance tests to assist you in 
fully evaluating your contemplated purchases, including the performance of 
that product when combined with other products.   
For more complete information visit www.intel.com/benchmarks.

Intel's compilers may or may not optimize to the same degree for non-Intel 
microprocessors for optimizations that are not unique to Intel microprocessors. 
These optimizations include SSE2, SSE3, and SSSE3 instruction sets and other optimizations. 
Intel does not guarantee the availability, functionality, or effectiveness of any 
optimization on microprocessors not manufactured by Intel. 
Microprocessor-dependent optimizations in this product are intended for use with 
Intel microprocessors. 
Certain optimizations not specific to Intel microarchitecture are reserved for Intel 
microprocessors. 
Please refer to the applicable product User and Reference Guides for more 
information regarding the specific instruction sets covered by this notice.  
Notice Revision \#20110804
\end{framed}

>>>>

% \balance
\begin{framed}
\scriptsize

\noindent \textbf{Notices \& Disclaimers}
\\

\noindent Intel technologies may require enabled hardware, software or service activation.
\\

\noindent No product or component can be absolutely secure.
\\

\noindent Your costs and results may vary.
\\

\noindent \copyright Intel Corporation.  Intel, the Intel logo, and other Intel marks are trademarks of Intel Corporation or its subsidiaries.  Other names and brands may be claimed as the property of others.
\\

\noindent Intel does not control or audit third-party data.  You should consult other sources to evaluate accuracy.
\\

\noindent Intel disclaims all express and implied warranties, including without limitation, the implied warranties of merchantability, fitness for a particular purpose, and non-infringement, as well as any warranty arising from course of performance, course of dealing, or usage in trade.

% \copyright  Intel Corporation.  Intel, the Intel logo, and other Intel marks are trademarks of Intel Corporation or its subsidiaries.  Other names and brands may be claimed as the property of others.

% Performance results are based on testing as of dates shown in configurations and may not reflect all publicly available security updates.  See backup for configuration details.  No product or component can be absolutely secure.

% Your costs and results may vary.

% Intel technologies may require enabled hardware, software or service activation.

\noindent Software and workloads used in performance tests may have been optimized for performance only on Intel microprocessors.  Performance tests, such as SYSmark and MobileMark, are measured using specific computer systems, components, software, operations and functions.  Any change to any of those factors may cause the results to vary.  You should consult other information and performance tests to assist you in fully evaluating your contemplated purchases, including the performance of that product when combined with other products.   For more complete information visit www.intel.com/benchmarks.
\\

\noindent Intel's compilers may or may not optimize to the same degree for non-Intel microprocessors for optimizations that are not unique to Intel microprocessors. These optimizations include SSE2, SSE3, and SSSE3 instruction sets and other optimizations. Intel does not guarantee the availability, functionality, or effectiveness of any optimization on microprocessors not manufactured by Intel. Microprocessor-dependent optimizations in this product are intended for use with Intel microprocessors. Certain optimizations not specific to Intel microarchitecture are reserved for Intel microprocessors. Please refer to the applicable product User and Reference Guides for more information regarding the specific instruction sets covered by this notice.  Notice Revision \#20110804
\end{framed}
